---
title: "PGR1 - Reproducible data"
---

# Peer graded assignment

Loading packages and data:
```{r setup}
#setwd("D:/Trabajo (3)/Métodos/R courses/Curso 5 DSE - Reproducible research/PGA1")
library(ggplot2)
furl <- "https://github.com/wilsonhb/RepData_PeerAssessment1/raw/master/activity.zip"
if(!file.exists("activity.zip")) {
      download.file(furl, destfile = "./activity.zip", mode="wb")
      unzip("activity.zip", overwrite = T)
}
da <- read.csv("D:/Trabajo (3)/Métodos/R courses/Curso 5 DSE - Reproducible research/PGA1/activity.csv", header = T)
```

# 1. What is the mean total number of steps taken per day?
Creates an object containing the collapse dataset:
```{r }
steps_day <- aggregate(steps ~ date, da, sum)
```

Creates the histogram:
```{r }
hist (steps_day$steps, main="Total number of steps per day", col="red", xlab="Number of steps")
ggsave("./instructions_fig/plot1.png")
```

Reporting the mean and median:
```{r }
mean(steps_day$steps)
median(steps_day$steps)
```


#2. What is the average daily activity pattern?
Making the time series plot for 5-minute interval
```{r }
steps_interval <- aggregate(steps ~ interval, da, mean)
g <- ggplot(data = steps_interval, aes(interval, steps))
g + geom_line() +
      labs(x="5-minute interval", y = "Steps (mean)") +
      labs(title = "Daily activity pattern") +
      theme_minimal()
ggsave("./instructions_fig/plot2.png")
```

The interval with the maximum of steps is:
```{r }
max_interval <- steps_interval[which.max(steps_interval$steps), 1]
max_interval
```

# 3. Imputing missing values
Calculate and report the total number of missing values in the dataset

##Total missing values:
```{r }
na <- sum(!complete.cases(da))
na
```

##Imputing missing values for NA:
```{r }
da$steps[is.na(da$steps) == T] <- mean(da$steps, na.rm = T)
sum(is.na(da$steps))
```

## Replicate histogram for daily steps with no NA
```{r }
da2 <- aggregate(steps ~ date, da, sum)
g <- ggplot(data = da2, aes(steps))
g + geom_histogram(bins = 30, col="green") +
      labs("Histogram of daily steps with no NA")
hist (da2$steps, main="Total number of steps per day", col="orange", xlab="Number of steps")
ggsave("./instructions_fig/plot3.png")
```

# 4. Are there differences in activity patterns between weekdays and weekends?
```{r }
library(timeDate)
#da <- read.csv("activity.csv", header = T)
#da$steps[is.na(da$steps) == T] <- mean(da$steps, na.rm = T)
da$ww2 <- isWeekday(da$date)
table (da$ww2)
library(lattice)
da2 <- aggregate(steps ~ interval + ww2, da, mean)
with(da2, xyplot(steps ~ interval | ww2, type="l", layout=c(1,2)))
#
g <- ggplot(da2, aes(interval, steps, color = ww2))
g + facet_wrap(.~ww2, ncol=1, nrow=2) +
      geom_line() +
      labs(x = "Interval", y= "Average number of steps") +
      labs(title = "Average daily steps during weekend/weekdays") +
      scale_colour_discrete(name="Days", labels=c("Weekend", "Weekdays"))
ggsave("./instructions_fig/plot4.png")
```
      
      
